Simulation of Nano Particles in a Laser Trap

### 2017-02-09 doc/draft2.tex

>>>>

\subsection{Measurement}
Now that the functionality of every individual part has been established, the main question can be tackled: how does the laser intensity influence the
center of mass motion of the nano particle? And which influence does the surrounding gas exert?\\
In order to investigate the origin of the motion of the center of mass, we first need to check whether the eHEX algorithm itself has any influence on
the center of mass motion. This is done by applying the algorithm without the thermostat and calculating the center of mass velocity. This turns out
to be the case, i.e. the center of mass motion stands still.\\
To check the integrity of the algortihm, a simple case needs to be tested. Such a simple case is $\Delta Q = 0$, i.e. no energy begin pumped into the
system. The expected outcome of this case is a thermal equilibration between the incoming gas particles, the outgoing gas particles and the center of
mass motion of the nano particle with the incoming gas temperature being the reference value. 
The measurement yields this result and backs up the claim. Furthermore, the internal temperature of the nano particle also equilibrates to the 
temperature of the surrounding gas. This was checked on a system with pressure $P=0.8$, temperature of the incoming particles $T_\text{imp} = 0.05$ 
and internal temperature of the nano particle (set with the velocity verlet) $T_\text{intern} = 0.2$. The resulting temperatures are:
\begin{eqnarray*}
    T_\text{em} = 0.0494 \pm 0.0009\\
    T_\text{COM} = 0.051 \pm 0.108\\
    T_\text{int} = 0.048 \pm 0.007\\
\end{eqnarray*}
